Neuro I

### 2017-08-03 neuro1.rmd
added sc

@@

>>>>

Anatomical site: bilateral is probably peripheral neuropathy.

Hx:

-  HPC: does it also occur in the hands? Also have to clarify if numb = tingling/weakness?

Ex: where exactly does it occur? Systemic or not?

DDx:

-  Diabetic neuropathy
-  Heavy metal toxicity
-  Alcohol
-  Nutritional disorders
-  GBS: often feel like they're walking on cotton

Other ANS involvement

-  Syncope/presyncope
-  Feeling hot/sweaty

Positive and negative symptoms:

-  Positive: might feel burning/tingling
-  Negative: loss of motor control, sensory, fine motor control

Pathology of peripheral neuropathies:

-  Axonal damage
-  Loss of myelination

Mononeuropathies:

-  Carpal tunnel syndrome
-  Tarsal tunnel
-  Bells palsy
-  Ulnar palsy: hitting funny bone

Ix: neuropathy screen (nerve conduction, biopsies, CSF (GBS)), bloods (FBC, CHEM20, antibodies (vasculitis)), fasting blood sugar

Mx for diabetes:

-  Diabetes: diet, metformin
-  Treatment of pain itself: antidepressents, anticompulsants (capsaicin, gabapentin)
-  Care of the foot:
-  Quit smoking

@@

Anatomical structures:

-  Carpal tunnel
-  Guillans tunnel
-  Unlikely cerebral hemispheres

DDx:

-  Carpal tunnel syndrome
-  Ganglion
-  Peripheral neuropathy
-  Injured nerve

Radiculopathy: other muscular and sensory deficits

Risk factors for carpal tunnel

-  Repeated wrist movements with force
-  Female: smaller carpal tunnel
-  40-60
-  Obesity

Diagnosis for carpal tunnel: hyperflexion test. Flex for 1 min and see if symptoms increase. Median nerve slow could be carpal tunnel syndrome.
